Contextual Combinatorial Cascading Bandits

### 2016-01-15 contextual combinatorial cascading bandits.tex
add two paragraphs for problem formulation in general case

>>>>

\section{Problem Formulation-general case}

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\cS$ be the set of \textit{feasible actions}. For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$. In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning. In social influence problem, a feasible action is a subset of people in graph structure. In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set. We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$. We assume all feasible actions considered in this paper have size at most $K$.

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm. \shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. Notice that the size of the action is not fixed. Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of base arms in $\bO_t \subset \bA_t$. For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.

We use random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$. Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
	\label{eq:expectation}
	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
